### 2018-10-30 pilot_manuscript.Rmd
Some formatting edits to manuscript

#Kavanaugh Supreme Court Hearing
In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice. Kavanaugh was previously on the U.S. Court of Appeals for the District of Columbia. The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD]. Following allegations of sexual assault by high school classmate Dr. Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.

@@

# Method

@@

# Results

@@

# Discussion
How it turned out

>>>>

##Kavanaugh Supreme Court Hearing
In the wake of Justice Anthony Kennedy's retirement from the Supreme Court of the United States, President Donald Trump nominated Brett Kavanaugh as the new Associate Justice. Kavanaugh was previously on the U.S. Court of Appeals for the District of Columbia. The Senate Judiciary Committee began his confirmation hearing on September 4, 2018 [@CITE_CONGRESSIONAL_RECORD]. Following allegations of sexual assault by high school classmate Dr. Christine Blasey Ford, the committee postponed its vote on whether or not to open the confirmation to the entire Senate.

@@

# Method - Experiment 1

@@

# Experiment 1 results

@@

# Method - Experiment 2

## Sources
Experiment 2 largely followed the same method as Experiment 1. Political articles specifically referring to Brett Kavanaugh and his Supreme Court confirmation hearing were scraped

# Experiment 2 results

# Discussion

## Experiment 1

## Experiment 2

## General discussion
How it turned out
